% LaTeX CV
\documentclass[final,a4paper,notitlepage,10pt]{report}

%%% Packages %%%
\usepackage[utf8]{inputenc}	% inputenc for encoding to utf8
\usepackage{auto-pst-pdf}	% auto-pst-pdf converts pst to pdf
\usepackage{pst-barcode}	% pst-barcode try implement QR code
\usepackage{multicol}	% multicol used for multiple columns
\usepackage[paper=a4paper,left=0.75cm,right=0.75cm,top=0.75cm,bottom=0.75cm,noheadfoot]{geometry}	% geometry for margins
\usepackage[hidelinks,breaklinks]{hyperref}	% hyperref for linking references for pdf
\usepackage{wrapfig}	% wrapfig to wrap text around figures
\usepackage{mdwlist}	% mdwlist for compact enumeration/list items
\usepackage[compact]{titlesec}	% titlesec for title section layout
\usepackage{mdwlist}	% mdwlist for compact enumeration/list items
\usepackage{multicol}	% multicol for multiple columns

% Rule settings
\hyphenpenalty=5000
\tolerance=1000

% for mailto command
\newcommand{\mailto}[1]{\href{mailto:#1}{#1}}

% change itemize to be compact
\makecompactlist{compactitemize}{itemize}

% Name and contact information
\newcommand{\name}{Daniel Lemon}
\newcommand{\addr}{158 Park Avenue, Barking, IG11 8QY, England}
\newcommand{\phone}{+44 785 241 2132}
\newcommand{\email}{\mailto{dan@danlemon.com}}
\newcommand{\website}{\href{http://danlemon.com}{http://danlemon.com}}
\newcommand{\github}{\href{https://github.com/dan2k3k4}{https://github.com/dan2k3k4}}
\newcommand{\twitter}{\href{https://twitter.com/dan2k3k4}{https://twitter.com/dan2k3k4}}

% tweak title spacing
\titlespacing{\section}{0pt}{*2}{*0}
\titlespacing{\subsection}{0pt}{*2}{*0}
\titlespacing{\subsubsection}{0pt}{*2}{*0}

% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1} 

% set paragraph indent to 0
\setlength\parindent{0pt}

% format section title with a nice center line
%\titleformat\section{\normalfont\large\centerline{\hss\rule{.7\textwidth}{.01em}\hss}}{\thesection}{.01em}{}

% set pagestyle to empty
\pagestyle{empty}

% begin actual CV
\begin{document}

% wrap whole top section in one textwidth minipage
\begin{minipage}[t]{\textwidth}
	\begin{minipage}{1in}
	\begin{pspicture}(1in, 1in)
	% The MECARD format is used to exchange contact information.
	% \psbarcode{MECARD:N:Lemon,Daniel;EMAIL:dan@danlemon.com;TEL:00447852412132;NOTE:Software Programmer;URL:http://danlemon.com;}{}{qrcode}
		\psbarcode{MECARD:N:Lemon,Daniel;EMAIL:dan@danlemon.com;TEL:00447852412132;URL:http://danlemon.com;;}{}{qrcode}
	\end{pspicture}
	\end{minipage}\hspace{0.6cm}% adjust for horizontal spacing
	\begin{minipage}{0.85\textwidth}
	\textbf{\LARGE \qquad \name }

	\begin{tabular*}{\textwidth}{@{} p{0.4\textwidth} l}\\
	\textit{Email:} \email\ & \textit{Address:} \addr \\
	\textit{Web:} \website\ & \textit{Mobile:} \phone \\
	\textit{GitHub:} \github\ & \textit{Twitter:} \twitter \\
	\end{tabular*}\\
	
	\end{minipage}
\end{minipage}

\section*{Personal Profile {\hfill\raisebox{.5ex}{\makebox[.65\textwidth]{\hrulefill}}}}
\begin{compactitemize}
\item Enthusiastic outgoing undergraduate with a determined outlook on enhancing software development projects by utilizing \textbf{agile methodologies} with a keen interest in open-source projects; currently studying Computer Science BSc (Hons) at Brunel University.

\item Currently investigating how educational gaming can be used as a channel of communication between international physics organisations (i.e. CERN) and A-level physics students through an \textbf{open-source android game}.

\item Actively participating in various programming related meet-up groups and attending numerous events as well as conferences. First undergraduate to be invited as an \textbf{assistant organizer} for the Graduate Developer Community.
\end{compactitemize}

\section*{Key Skills {\hfill\raisebox{.5ex}{\makebox[.65\textwidth]{\hrulefill}}}}
{\bf Technical}
\vspace*{-0.5\baselineskip}
\begin{compactitemize}
	\item \textbf{Java} (intermediate): Currently building final year project as a educational android game.\\
	Built an open-source GUI based XML-editor based on an older tool; \textbf{re-engineered} it to produce PLC (Programmable Logic Controller) code over an NFS network as well as implemented other features like a custom file lock system for the IEPLC project in CERN.\\
	Produced \textbf{open-source modifications} for Call of Duty 4 (PC) within a team of 4; ensuring everything was packed together for regular monthly releases.
	\item \textbf{C++} (beginner): Built a simple command line program to analyse different mathematical functions. Completed some \textbf{Project Euler} problems in C++.
	\item \textbf{Javascript} (beginner): Currently participating in \textbf{Code Year} by completing a new set of Javascript courses each week for a full year.
	\item \textbf{\LaTeX}\ (intermediate): Completed University coursework reports in \LaTeX\ as well as this CV and personal business cards.
	\item \textbf{Others:} Drupal, HTML5, CSS3, PHP, Prolog, SQL (MySQL), jQuery.
	\item \textbf{Agile:} Experienced use of issue and bug tracking software such as \textbf{JIRA}, actively seek to develop by iterative protoyping, break-down tasks into weekly Sprints (Scrum) and follow the Agile Manifesto.
	\item \textbf{Tools:} Eclipse, Android SDK, Netbeans, Git, Subversion, ant, Maven, jUnit, cron.
	\item \textbf{Operating Systems:} Windows XP/7 and Windows Server 2003, Linux (Ubuntu, Scientific Linux CERN 5, and Redhat).
\end{compactitemize}

{\bf Languages:} \qquad \textbf{English} (native) \quad \textbf{French} (intermediate; fluent) \quad \textbf{Bulgarian} (beginner; can read and write Cyrillic)

\section*{Education {\hfill\raisebox{.5ex}{\makebox[.65\textwidth]{\hrulefill}}}}
\vspace*{-\baselineskip}
\begin{tabular*}{\columnwidth}{@{} p{0.2\textwidth} l @{\extracolsep{\fill}} r }\\
Sep ’08 - Jun ‘12 & {\bf Computer Science BSc, Brunel University} \textit{(predicted} \textbf{1st class}\textit{)} & London, England \\
\multicolumn{3}{@{} p{\textwidth}}{
Built a GUI based Java tool to demonstrate and visually compare different sort algorithms. Built a command line game in Java to demonstrate object orientation.\newline
Key modules: \textbf{Artificial Intelligence}, \textbf{Software Engineering}, Software Project Management, Advanced Topics in Computer Science, Computation, Algorithms \& Implementation.
}\\
\end{tabular*}\\[-0.5\baselineskip]
\begin{tabular*}{\columnwidth}{@{} p{0.2\textwidth} l @{\extracolsep{\fill}} r }\\
Sep ’07 - Jun ‘08 & {\bf Foundations of Information Technology, Brunel University} & London, England\\
\multicolumn{3}{@{} p{\textwidth}}{
Built a command line tool to demonstrate different mathematical functions in C++.
}\\
\end{tabular*}\\[-0.5\baselineskip]
\begin{tabular*}{\columnwidth}{@{} p{0.2\textwidth} l @{\extracolsep{\fill}} r }\\
Sep ’99 - Jun ‘06 & {\bf Canon Palmer Catholic School} & London, England\\
\multicolumn{3}{@{} p{\textwidth}}{
Graduated with Advanced Level certificates in: \textbf{Information Communication Technology} (C), \textbf{Mathematics} (D) and \textbf{Physics} (E), including AS-Level in \textbf{Business Studies} (C).\newline
Achieved 10 GSCE’s between A to C grades including high grades in: Mathematics, Science, Business Studies, English and Computing.
}\\
\end{tabular*}

\section*{Industrial Placement {\hfill\raisebox{.5ex}{\makebox[.65\textwidth]{\hrulefill}}}}
\vspace*{-\baselineskip}
\begin{tabular*}{\columnwidth}{@{} p{0.2\textwidth} l @{\extracolsep{\fill}} r }\\
Jun '10 - Jul '11 & {\bf Technical Student, CERN} & Geneva, Switzerland\\
\end{tabular*}\\
\vspace*{-\baselineskip}
\begin{compactitemize}
\item Involved with designing, building and implementing a working \textbf{GUI-based XML-Editor} that produced PLC (Programmable Logic Controller) code and utilizes the NFS network for storage. It was a large project and is used to help the engineers produce PLC code in a shorter period of time without needing expert knowledge of a PLC.
\item Extensive use of Agile methodology; development progression via \textbf{iterative prototyping}, continuous code refactoring including implementing some features of Scrum such as a weekly sprint of tasks to-do, tasks currently being done, and completed tasks.
\item Included development work in Java, XML and Python; as well as integrating ant build scripts and updating the code-base under, subversion, a version control system.
\item Worked with supervisor on initial project planning; different clients would request feature changes and submit bug reports via \textbf{JIRA}. Also worked alongside many French speaking employees and took two French learning courses to increase personal knowledge of the language.
\item Parallel to building the project, involved with providing aid in the running and organising of social events for students under 30 years old. Organised monthly \textbf{networking} event for new arrivals to CERN and invite everyone so that the new people would easily integrate with others.
\item CERN offers every employee the chance to expand their knowledge on any platform domain so it was easy to self educate about different technologies such as XML, XPATH, Python, and Agile development.
\end{compactitemize}

\section*{Employment {\hfill\raisebox{.5ex}{\makebox[.65\textwidth]{\hrulefill}}}}
\vspace*{-\baselineskip}
\begin{tabular*}{\columnwidth}{@{} p{0.2\textwidth} l @{\extracolsep{\fill}} r }\\
Apr ‘10 - May ‘10 & {\bf Freelancer, Mikamai} & London, England\\
\multicolumn{3}{@{} p{\textwidth}}{
Updating the company's website to include a new portfolio layout using an open-source CMS (content management system) platform. Also tasked with updating the Wordpress blog layout and implementing Facebook as well as managing the Facebook page to increase brand awareness.
}\\
Sep '09 - Dec '09 & {\bf Freelancer, Diffiniti} & London, England \\
\multicolumn{3}{@{} p{\textwidth}}{
Working with a team of people who specialise in Search Engine Optimization (SEO) for various large clients. Work involved submitting client information to on-line directories, clients involved: Sky and AutoTrader.
}\\
Nov ‘06 - Aug ‘07 & {\bf Busser, The Old Spaghetti Factory} & Whistler, BC, Canada \\
\multicolumn{3}{@{} p{\textwidth}}{
Clearing and resetting tables as fast as possible to ensure a quick turnover of customers to the restaurant.
}\\
Nov ‘06 - Jul ‘07 & {\bf Sandwich Artist, Subway} & Whistler, BC, Canada\\
\multicolumn{3}{@{} p{\textwidth}}{
Constructing professional looking sandwiches to a customers' expectation with a high level of cleanliness.
}
\end{tabular*}

\section*{Volunteer Experience {\hfill\raisebox{.5ex}{\makebox[.65\textwidth]{\hrulefill}}}}
\vspace*{-\baselineskip}
\begin{tabular*}{\columnwidth}{@{} p{0.2\textwidth} l @{\extracolsep{\fill}} r }\\
Aug '11 - Aug '11 & {\bf Global Hope Network Short Term Team} & Dire Dawa, Ethiopia, Africa \\
\multicolumn{3}{@{} p{\textwidth}}{
Spent a week volunteering with some of the world's poorest. Involved working with building communities between 3 different villages by organising football matches and creating dialogue with the village elders.
}\\
Oct '06 - May '07 & {\bf Whistler Village Host} & Whistler, BC, Canada \\
\multicolumn{3}{@{} p{\textwidth}}{
Providing way finding assistance to visitors as well as information and history of the village.
}\\
Oct '06 - Dec '06 & {\bf Maurice Young Millennium Place} & Whistler, BC, Canada \\
\multicolumn{3}{@{} p{\textwidth}}{
Verifying event tickets on the door as well as helping to set-up or dismantle the theatre stage.
}\\
Nov '06 - Dec '06 & {\bf Whistler Film Festival} & Whistler, BC, Canada\\
\multicolumn{3}{@{} p{\textwidth}}{
Interviewed people and conducted surveys around the village to record peoples' feelings of the festival.
}
\end{tabular*}

\section*{Interests \& Activities {\hfill\raisebox{.5ex}{\makebox[.65\textwidth]{\hrulefill}}}}
\begin{compactitemize}
\item \textbf{Young @ CERN \& Technical Student Social Organizer}. Organised and managed monthly social events for the students working in CERN. This helped to build a community between the students \& improved social interactions.
\item Participated in \textbf{Start-up Weekend Geneva 2010}, involved with a team that aimed at creating a fashion company by re-using unsold products from large clothing distributors and \textbf{Start-up Weekend Lausanne 2011}, involved in a team that aimed at building a geo-localisation application focused on providing local shopping deals. The Start-up Weekend events focus on building a start-up company from idea to demo over a 56-hour period in one weekend.
\item \textbf{Assistant Organizer for the Graduate Developer Community}, help to create and schedule new events with the other organizers. Attended various events including an introduction to using Agile methodology.
\item Member of the \textbf{London Java Community}, attended various different events as well as being a member of several other meet-up groups such as: London Android Group, PHP London Group and Facebook Developers Garage London.
\item Attended DroidCon 2011, an \textbf{Android developers conference}, TEDxGeneva 2011, LiFT 2011, and participated in open-source start-up events aimed at teaching students how to get started with an open-source project: from how to commit changes; to forking for building new features.
\item Avid \textbf{snowboarder}, member of the Brunel Snow Club and past member of the CERN Ski Club.
\item Thoroughly enjoy \textbf{travelling}; spent a year in Whistler, Canada and another year in France; snowboarded in Slovakia, France, Italy, Switzerland; visited Spain, Bulgaria, America, Ethiopia, and Kenya.
\end{compactitemize}

\section*{References {\hfill\raisebox{.5ex}{\makebox[.65\textwidth]{\hrulefill}}}}
Available on request

\end{document}
